The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multi-Phase Forest Inventories

### 2017-09-21 JStatSoft_forestinventory_master-concordance.tex
update AndreasAlex 21.09.2017

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 107 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 115:%
1 97 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 213:%
123 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 223:%
1 132 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 356:%
134 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 368:%
1 201 1 1 4 1 1 1 2 1 0 2 1 3 0 1 2 2 1 1 3 14 0 1 2 16 1 1 5 7 0 1 2 4 1 1 2 24 0 1 2 6 1 1 2 4 0 1 2 4 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 157 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 5 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1004:%
147}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 1005:%
1 119 1 1 2 8 0 1 2 4 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 4 1 1 4 6 0 1 2 2 1 1 2 8 0 1 2 193 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 11 0 1 3 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 7 1 1 7 10 0 1 3 2 1 1 2 12 0 1 2 6 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1524:%
149 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1536:%
1 42 1 1 2 11 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1601:%
162 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1611:%
1 20 1 1 2 4 0 1 2 4 1 1 6 8 0 1 2 4 1 1 6 8 0 1 2 18 1 1 8 16 1 1 7 9 0 1 2 2 1 1 2 8 0 1 2 2 1 1 2 8 0 1 2 4 1 1 2 8 0 1 2 22 1 1 3 5 0 1 2 27 1 1 3 5 0 1 2 39 1 1 3 5 0 1 2 23 1 1 3 5 0 1 2 19 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1908:%
173 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1918:%
1 20 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 2149:%
184 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 2158:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 2163:%
194 11 1}

>>>>

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 107 1 1 4 1 1 1 4 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 115:%
1 97 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 213:%
123 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 223:%
1 132 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 356:%
134 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 368:%
1 201 1 1 4 1 1 1 2 1 0 2 1 3 0 1 2 2 1 1 3 14 0 1 2 16 1 1 5 7 0 1 2 4 1 1 2 24 0 1 2 6 1 1 2 4 0 1 2 4 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 133 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 7 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 982:%
147}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 983:%
1 119 1 1 2 8 0 1 2 4 1 1 2 1 0 1 1 3 0 1 2 4 1 1 4 1 1 1 6 8 0 1 2 2 1 1 2 27 0 1 2 4 1 1 4 6 0 1 2 2 1 1 2 8 0 1 2 193 1 1 3 2 0 1 1 3 0 1 2 4 1 1 8 11 0 1 3 1 1 1 4 1 1 1 2 12 0 1 2 4 1 1 7 9 0 1 2 2 1 1 2 12 0 1 2 7 1 1 7 10 0 1 3 2 1 1 2 12 0 1 2 6 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1502:%
149 11 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 1514:%
1 42 1 1 2 11 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1579:%
162 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1589:%
1 20 1 1 2 4 0 1 2 4 1 1 6 8 0 1 2 4 1 1 6 8 0 1 2 18 1 1 8 16 1 1 7 9 0 1 2 2 1 1 2 8 0 1 2 2 1 1 2 8 0 1 2 4 1 1 2 8 0 1 2 22 1 1 3 5 0 1 2 27 1 1 3 5 0 1 2 39 1 1 3 5 0 1 2 23 1 1 3 5 0 1 2 19 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1886:%
173 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1896:%
1 20 1 1 4 6 0 1 2 3 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 7 9 0 1 2 2 1 1 8 10 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 2127:%
184 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 2136:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 2141:%
194 11 1}

### 2017-09-21 rnw/Main structure and modules of the Package.Rnw
update AndreasAlex 21.09.2017

Most forest inventories gather the field information by randomly or systematically selecting points in the forest area defined by coordinates to which inventorists are sent. At these points, the inventorist measures sample trees located within a constructed circle (called sample plot) around the sample point $x$, and aggregates their individual characteristics (e.g. their individual timber volumes) to local plot densities (e.g. the timber volume density in $m^3/ha$). The estimators implemented in the \pkg{forestinventory} package use the so called \textit{infinite population approach} in order to bridge this sampling process to the mathematics behind the estimators. The infinite population approach assumes that the spatial distribution of the local density, $Y(x)$, over the forest area is determined by a mathematical continuous function, as visualized in Figure \ref{fig:inf_pop_apr}. The \textit{population total} of the target variable (e.g. the total timber volume of the forest) is mathematically equivalent to the integral of that density function, which defines the volume under the green surface in Figure \ref{fig:inf_pop_apr}. From this perspective, the challenging part of an inventory is that the form of this function, and thus $Y$, is unknown. Theoretically, we still could get $Y$ by observing the function value, i.e. the local density $Y(x)$ at each possible point $x$ over the function plain (i.e. the forest area) and sum those obervations up. However, we see at the first spot that this is impossible, because the number of function values $Y(x)$ and thus the number of possible sample points $x$ is $infinite$. So we are left with only a sample of $Y(x)$ from an infinite population of sample points in order to \textit{estimate} the integral $Y=\frac{1}{\lambda(F)}\int_{F}Y(x)dx$ by $\hat{Y}$. All estimators included in the \pkg{forestinventory} package basically rest upon this theoretical approach. A key point for practical implementation is that in the infinite population approach, a local density value $Y(x)$ is a point information associated to the sample point $x$, which constitutes the sample unit, but not to the sample plot area. This has some obvious practical advantages over the finite population approach, where the sample units actually are cirular or rectangular plots. One is the impossibility of a perfect tesselation of an amorphous forest area by any kind of plot-shape, and hence, the population in the finite approach is, strictly speaking, not defined. The consideration of an underlying infinite population of sample points will also play an important role when incorporating auxiliary information in the frame of two- and three-phase estimation methods.

\begin{figure}[htb]
\centering
\resizebox{0.5\hsize}{!}{\includegraphics{fig/OnePhase.png}}
\caption{Viisualization of the infinite population approach. The spatial distribution of a hypothetical density function for every point in a forested area is represented as wavy green surface.  Sample plots (grean circles) inform the inventorist of the value of the density function at that point.}
\label{fig:inf_pop_apr}
\end{figure}

@@

\begin{figure}[htb]
\centering
\resizebox{1\hsize}{!}{\includegraphics{fig/Package_structure_3.eps}}
\caption{Structure of the multi-phase estimators in the \proglang{R} package \pkg{forestinventory}}
\label{fig:struct_package}
\end{figure}

>>>>

Most forest inventories gather the field information by randomly or systematically selecting points in the forest area defined by coordinates to which inventorists are sent. At these points, the inventorist measures sample trees located within a constructed circle (called sample plot) around the sample point $x$, and aggregates their individual characteristics (e.g. their individual timber volumes) to local plot densities (e.g. the timber density in $m^3/ha$). The estimators implemented in the \pkg{forestinventory} package use the so called \textit{infinite population approach} in order to bridge this inventory process to the mathematics behind the estimators. The infinite population approach assumes that the spatial distribution of the local density, $Y(x)$, over the forest area is determined by a piecewise constant function, as visualized in Figure \ref{fig:inf_pop_apr}. The \textit{population total} of the target variable (e.g. the total timber volume of the forest) is mathematically equivalent to the integral of that density function, which is depicted in Figure \ref{fig:inf_pop_apr} as the volume under the density surface. From this perspective, the challenging part of an inventory is that the form of this function is unknown. Theoretically, we still could get the total timber volume by observing the function value, i.e. the local density $Y(x)$, at each possible point $x$ over the forest area and sum those obervations up. However, this is impossible because there is an infinite number of points in the forest area. Our strategy is thus to take a sample of points, $s_2$, from an infinite population of possible points and use their associated local densities, i.e. $Y(x)$, to \textit{estimate} the integral $Y=\frac{1}{\lambda(F)}\int_{F}Y(x)dx$ with $\hat{Y}=\frac{1}{n_2}\sum_{s_2}Y(x)$.  The total timber volume can then be obtained by multiplying $\hat{Y}$ by the surface area of the forest, $\lambda(F)$.  All estimators included in the \pkg{forestinventory} package basically rest upon this theoretical approach. A key point for practical implementation is that in the infinite population approach, a local density value $Y(x)$ is associated with the sample point $x$, which constitutes the sample unit, and not to the sample plot area. This has some obvious theoretical advantages over the finite population approach, where the sample units actually are cirular or rectangular plots. One is the impossibility of a perfect tesselation over an amorphous forest area by any kind of plot-shape, and hence, the population in the finite approach is, strictly speaking, not perfectly defined with respect to the forest area. The consideration of an underlying infinite population of sample points will also play an important role when incorporating auxiliary information in the frame of two- and three-phase estimation methods.

\begin{figure}[htb]
\centering
\resizebox{0.42\hsize}{!}{\includegraphics{fig/localdensity_final-01.eps}}
\caption{Artificial representation of local density surface. The spatial distribution of a hypotheticaldensity function for every point in a forested area is represented as wavy stepwise constant green surface.  Sample plots (white dots) inform the inventorist of the value of the density function at that point.}
\label{fig:inf_pop_apr}
\end{figure}

% "we are sampling values of a function that is defined by the spatial arrangement of the trees"

@@

\begin{figure}[htb]
\centering
\resizebox{0.95\hsize}{!}{\includegraphics{fig/Package_structure_3.eps}}
\caption{Structure of the multi-phase estimators in the \proglang{R} package \pkg{forestinventory}}
\label{fig:struct_package}
\end{figure}
